Oregon GWR smoke association with Cardiopulmonary Emergency Room visits

### 2018-05-30 r_scripts/analysis/oregon_wfs_ed_results.Rmd
fixed markdown file to comment out file save.

# print plot
ggsave(filename = "./r_scripts/analysis/Figs/cardiopulmonary_er_result.tiff", 
       plot = result_plot, 
       units="in", width=8, height=6, dpi=300)

>>>>

# print plot
#ggsave(filename = "./r_scripts/analysis/Figs/cardiopulmonary_er_result.tiff", 
#       plot = result_plot, 
#       units="in", width=8, height=6, dpi=300)
